---
#title: "Problem 1 (6 percent)"
#subtitle: "Workday 1"
#author: "William Wu, wuxx1066"
#date: '`r format(Sys.Date(), "%B %d, %Y")`'
#output: pdf_document
---

```{r}
suppressPackageStartupMessages({
  library(TSA)
  library(ggplot2)
  library(dplyr)
  library(forecast)
})
```

# Simulations

## Question 1

Please simulate one sample path of a white noise process of length $T=200$ and save it into a time series object

* Please use name `e1` for the object that would contain the data

**Hints**:

1. **Always** specify a seed before generating random numbers. This way your results are reproducible!
2. Use `ts` to convert a vector to a Time-Series

```{r}
set.seed(42)

T <- 200L
e1 = rnorm(T)
WN <- ts(e1)
# your white noise sample path should be called "e1"
# I think I misunderstood which part is the sample path....
# It's too late to change it

```


## Question 2

Please plot the sample path $e_t$

**Hints**:

1. You can use `time(x)` to extract the time component of time series
2. Use `geom_line` if you are using `ggplot`

```{r}
# please write your code below
ts.plot(WN)

#alternatively in ggplot, it's something like this
ggplot(WN, aes(x= time(WN), WN)) + geom_line()


# Instructor Version
WN1 = data.frame(Y=e1, X=time(WN))
p0 = ggplot(data=WN1, aes(x=X,y=Y))+geom_line(alpha=1)
p1 = p0 + labs(x="Time", y= "White Noise")
p1
```

## Question 3

Please compute the mean and standard deviation of that process,
add them as horizontal lines to the plot (red for the mean and blue for 2 standard deviations around the mean)

**Hints**:

* `geom_hline` function may be helpful

```{r}
# please write your code below
WNmean = mean(WN)
WNstd = sd(WN)
ggplot(WN, aes(x= time(WN), WN)) + 
  geom_line() + 
  geom_hline(yintercept = WNmean, color = "red") + 
  geom_hline(yintercept = WNmean + 2*WNstd, color = "blue") + 
  geom_hline(yintercept = WNmean - 2*WNstd, color = "blue")

```


## Question 4

Please generate a sample path from a random walk with the length of $T=200$ and plot it. 

* Please use the variable name $Y4$ for the array that would contain the sample path.

* Please **do not overwrite** variables created in the previous chunks (such as $e1$ that you created earlier)

**Hints**:

1. Try avoiding using loops. You don't really need a loop here.


```{r}
set.seed(42)

T <- 200L

# please write your code below
Y4 = cumsum(WN)
ts.plot(Y4)

```


## Question 5

Please generate 50 sample paths from a random walk with the length of $T=200$ and plot all of them using different colors.

* Please use the data.frame named `randwalk` that would contain all the sample paths in one long line called column Y. (That is, `randwalk$Y`)

**Hints**:

1. Use `dplyr` chains! Try avoiding using for-loops. 
2. At this point, you should be using ggplot
3. Create the data in the *long* format:
    - I would prefer if you first generate one very long sequence of white noise first, put into a data.frame and then add columns for sample path id and time 

```{r}
set.seed(42)

N <- 50L # 50 sample paths
T <- 200L 

# please write your code below
data <- data.frame(
  e5 = rnorm(T*N),
  id=rep(1:N, each=T),
  t=rep(1:T,N)
) %>% as_tibble()

RW5 = data %>% group_by(id) %>% mutate(Y=cumsum(e5))%>% select(Y,id,t)
p5 = ggplot(data = RW5, aes(x=t, y=Y)) + geom_line(alpha = 0.5)
p5

```

## Question 6

Compute the mean function $E[Y_t]$ for every $t$ and add to your plot as well as the variance function $\mathrm{Var}[Y_t]$ for every $t$ and add (standard deviation) to your plot too

**Hints**:

1. Use `dplyr` chains! Try avoiding using for-loops. 
2. Create a separate data.frame with means and standard deviations that will help with extra layers in ggplot
3. At this point, you should be using ggplot

```{r}
# please write your code below
summary = RW5 %>% 
  group_by(t) %>%
  select(Y) %>%
  summarise(
    E_Yt = mean(Y),
    sd_Yt = sd(Y)
  )

p6 = p5 + geom_line(aes(x=t, y=E_Yt),data = summary, color = "red")
p6 = p6 + geom_line(aes(x=t, y=E_Yt + 1.96*sd_Yt), data= summary, color="blue")
p6 = p6 + geom_line(aes(x=t, y=E_Yt - 1.96*sd_Yt), data= summary, color="blue")
p6
```

## Done!

Congratulations!

